\propertitle

### 2019-11-15 maxNt_v6.tex
update

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-11-15T15:15:50+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Maximum-entropy distributions for a 
  neuronal network\\ from subnetwork data {\large\color{myred}[draft]}%\\{\large ***}%
}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Maximum-entropy from sample data}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

Let us translate this question into more precise terms first, because
\enquote{cooperativity}, \enquote{interaction}, and similar notions are
vague. A translation in terms of \emph{informational sufficiency} seems to
suit all these notions \parentext{for an intuitive understanding of
  sufficiency, which goes back to \cite{fisher1922}, see \eg\
  \cite[\sect~4.5]{bernardoetal1994}; \cite[\chap~8,
  \sect~14.2]{jaynes1994_r2003}; \cite{cifarellietal1982};
  \cite{kullbacketal1951}. For technical results and connections with the
  notion of symmetry see \eg\
  \cite{darmois1935,neyman1935,koopman1936,pitman1936,halmosetal1949,bahadur1954,berk1972,lauritzen1974,cifarellietal1980,cifarellietal1981,diaconisetal1981,lauritzen1982_r1988,diaconis1992,furmanczyketal1998,fortinietal2000,nogalesetal2000,kallenberg2005,lauritzen2007,ayetal2015}}.
The idea is as follows. We want to assess our degree of belief about the
frequencies of the activities of the sample, or about the activity of the
sample in a new time bin. For this assessment we should use all measured
data we have. But it sometimes happens that dropping part of the data --
for example, the measured third- and higher-order moments -- leaves our
assessment almost unchanged: the dropped data are \emph{informationally
  irrelevant}, or almost so. The remaining data -- for example, first and
second moments -- are then \emph{informationally
  sufficient}. % This informational quasi-sufficiency is interesting because
% it may give clues about network organization and dynamics.

We can approximately check how much a part of the data is irrelevant by
simply dropping it from the conditional of our degree of belief, and see
if the latter changes appreciably. When our degree of belief is built with
the maximum-entropy method, we simply drop part of the data used as
constraints and see how the resulting distribution changes. For example, we
may only retain the first two moments (means and correlations) or the first
four moments.

>>>>

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-11-15T15:18:17+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Maximum-entropy distributions for a 
  neuronal network\\ from subnetwork data {\large\color{myred}[draft]}%\\{\large ***}%
}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Maximum-entropy from sample data}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

Let us translate this question into more precise terms first, because
\enquote{cooperativity}, \enquote{interaction}, and similar notions are
vague. A translation in terms of \emph{informational sufficiency} seems to
suit all these notions \parentext{for an intuitive understanding of
  sufficiency, which goes back to \cite{fisher1922}, see \eg\
  \cite[\sect~4.5]{bernardoetal1994}; \cite[\chap~8,
  \sect~14.2]{jaynes1994_r2003}; \cite{cifarellietal1982};
  \cite{kullbacketal1951}. For technical results and connections with the
  notion of symmetry see \eg\
  \cite{darmois1935,neyman1935,koopman1936,pitman1936,halmosetal1949,bahadur1954,berk1972,lauritzen1974,cifarellietal1980,cifarellietal1981,diaconisetal1981,lauritzen1982_r1988,diaconis1992,furmanczyketal1998,fortinietal2000,nogalesetal2000,kallenberg2005,lauritzen2007,ayetal2015}}.
The idea is as follows. We want to assess our degree of belief about the
frequencies of the activities of the sample, or about the activity of the
sample in a new time bin. For this assessment we should use all measured
data we have. But it sometimes happens that dropping part of the data --
for example, the measured third- and higher-order moments -- leaves our
assessment almost unchanged: the dropped data are \emph{informationally
  irrelevant} or almost so. The remaining data -- for example, first and
second moments -- are then \emph{informationally
  sufficient}. % This informational quasi-sufficiency is interesting because
% it may give clues about network organization and dynamics.

We can approximately check how much a part of the data is irrelevant by
simply dropping it from the conditional of our probability, and see if the
latter changes appreciably. When our degree of belief is built with the
maximum-entropy method, this is done by dropping part of the constraints
and see how the resulting distribution changes. For example, we may only
retain the first two moments (means and correlations) or the first four
moments.
